% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{amstext}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{url}
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage{makecell}
\usepackage{verbatim}
\usepackage{listings}
\usepackage{wrapfig}
\usepackage{paralist}
\usepackage{xspace}
\usepackage{color}
\usepackage{times}
\usepackage{proof}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{color}
\usepackage{capt-of}
\usepackage[justification=centering]{caption}

\lstset{%
	language=C,
	basicstyle=\sffamily,
	commentstyle=\ttfamily,
	showstringspaces=false,
	escapeinside=``,
}

%\lstset{
%language=C,
%basicstyle=\small\sffamily,
%frame=tb,
%columns=fullflexible,
%showstringspaces=false
%}

\setcounter{secnumdepth}{4}

\usepackage[colorinlistoftodos,bordercolor=white]{todonotes}

\input{macros}

% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{Behavioral fault modeling and analysis with SBIP: \\ A Wheel Brake System Case Study\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Princeton University, Princeton NJ 08544, USA \and
Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
\email{lncs@springer.com}\\
\url{http://www.springer.com/gp/computer-science/lncs} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Behavior-Interaction-Priority(BIP) is a component-based framework for modeling complex systems. According to BIP framework, system can be represented by a set of components specifying the behavior which is synchronized and communicated by connectors that corresponds to subset of interactions.
Behavioral fault modeling and analysis refers to an integration of model based system design and safety analysis. In this paper, we integrate fault-tree-based safety analysis into BIP model and using statistical model checking engine for the BIP framework(SBIP) to offer a stochastic information to components and the entire system. By using SBIP with statistic model checking, we verify system specification and calculate probability of fault issues. We also trace the simulation result to confirm the extended system model without fault keeps consistence of the norminal system model.  
We illustrate an airplane wheel brake system meeting the industry standards as case study to show its advantage in analyzing fault behavior of safety-critical systems in aerospace practice.

\keywords{Model Checking  \and Safety Analysis \and Fault Tree \and BIP.}
\end{abstract}
%
%
%
\input{intro}

\input{rsdbip}

\section{Behavioral fault modeling}
\label{rsc:bfm}

\subsection{Fault-tree analysis}
Giving introdution of fault tree and its semantics.

\subsection{Fault-tree-based safety model in BIP}
Giving approach of interating fault-tree and BIP model.

\section{Aerospace case study}
\label{rsc:casestudy}

\subsection{Overview of Wheel Brake System}
Giving introdution of AIR6110 standards and Wheel Brake System, including fault tree and system architecture.

\subsection{WBS system model aspect}
Giving WBS system model aspect, including fault tree and norminal system model and fault model, table with modeling matrics and sample BIP code.

\subsection{Formal verification and analysis in SBIP}
Giving requirements and specification, using SBIP to do verification and analysis, comparing about norminal system model and fault model, results of formal verification including fault tree results with probability.

\section{Conclusion}
\label{rsc:conclusion}
Giving conclusion.

\section{Future work}
\label{rsc:futurework}
Giving futurework.

%
% the environments 'definition', 'lemma', 'proposition', 'corollary',
% 'remark', and 'example' are defined in the LLNCS documentclass as well.
%
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}
\bibitem{ref_article1}
Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)

\bibitem{ref_lncs1}
Author, F., Author, S.: Title of a proceedings paper. In: Editor,
F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
Springer, Heidelberg (2016). \doi{10.10007/1234567890}

\bibitem{ref_book1}
Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
Location (1999)

\bibitem{ref_proc1}
Author, A.-B.: Contribution title. In: 9th International Proceedings
on Proceedings, pp. 1--2. Publisher, Location (2010)

\bibitem{ref_url1}
LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
Oct 2017
\end{thebibliography}
\end{document}
