\section{Related Work}
Model-Based Safety Analysis (MBSA) is proposed by\cite{mbsa05}, aiming to generate failure injected models for both design and safety engineers to use. The study with Model-Based Safety Analysis has been ongoing for years. \cite{mbsa11} distinguishes MBSA construction approaches into two categories: performing MBSA on the extension of the models used in development process or on the basis of dedicated models defined by safety engineers.

As an example of the first kind of apporach, the ESACS and ISAAC project develops Extended System Model and Failure Injection methods\cite{erts06,esrel03}. Under this approach, safety engineers extend the design models from the development process with failure mode models. This approach maximizes the consistency between system development and safety analysis. However, a complete extended system may be intractable with analysis tools. The second approach to MBSA allows engineers to create model specifically for the goal of safety assessment. Using this approach, engineers can avoid unnecessary complexity by adjusting the level of detail. Modelling tools such as HiP-HOPS and AltaRica are used to build models for failure analysis specifically following this approach. 

%As a high level modelling language dedicated to Safety Analysis, AltaRica 

%\cite{imbsa14} propose a practical modelling methodology based on Altarica.

A number of tools have been extended to support both kinds of MBSA approaches, e.g. Architecture Analysis and Design Language (AADL)\cite{cmu07,sae11} and the integration of HiP-HOPS with Matlab Simulink\cite{dsn01}. \cite{aadl13} propose a dialect of AADL to validate failure injected model, using a satellite system as case study. With the development of the revised Error Model (EMV2) Annex\cite{aadlemv2} for AADL, engineers have applied AADL on different systems (e.g., Flight Control\cite{field1}, Fire Alarm\cite{field2} and other cyber-physical systems\cite{field3}) to capture key features of failure/error propagations from system models. In practice, engineers tend to use a variety of tools. \cite{aadl_altarica} propose a translator from AADL to AltaRica and apply it on a flight control system.\cite{aadl_hiphop} transform an AADL model of temperature monitoring system to into HiP-HOPS for analysis. To date, no tool has demonstrated absolute advantages over other tools in performing MBSA.
